A neural coarse graining theory of consciousness

### 2018-10-25 Paper_neural_coarse_graining_of_consciousness.tex
Change a lot of macro

% Meaning of colours --------------------------------------------------------- %
%	Red: Important and Critical
%	Orange: Todo
%	Blue: Topic and Guideline
%	Purple: Murmur, talking to myself
%	Green: Question, Call for help, Open for opinions and comments
%	Brown: Need Wording 
% ---------------------------------------------------------------------------- %

@@

% Funcitonal content
	% Quotes
		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}

	% todo
		% figure
		\newcommand{\includegraphicsTodo}[2][]{%
			\tcbox[%
				adjusted title=\LARGE To Be Modified,
				halign title=right,
				colbacktitle=Orange!75!White,
				coltitle=Black,
				colframe=Red!60!White,
				boxrule=1mm,
				colback=white%
				]{\includegraphics[#1]{#2}}}

	% Highlight
		\newcommand{\highlight}[2][Yellow]{\colorbox{#1}{#2}}

		% Highlight and comment
		\newcommand{\highlightAndComment}[3][Yellow]{\todo[color=#1]{#3}\colorbox{#1}{#2}}

@@

	% Need reference 
		\newcommand{\needref}[1]{%
			\ifthenelse{\equal{#1}{}}{%
				\todo[color=White, linecolor=BlueViolet]{\textcolor{BlueViolet}{Ref}}}{%
				\todo[color=White, linecolor=BlueViolet]{\textcolor{BlueViolet}{Ref: #1}}%
				}%
		}

	% idea
		% text idea
			\newcommand{\idea}[2][Plum]{\noindent
				\textcolor{#1}{[[ #2 ]]}}

		% box idea
			\newcommand{\ideaBox}[1]{
				\begin{tcolorbox}[hyphenationfix, width=12cm, colback=Thistle!50!white, flush right]
					#1
				\end{tcolorbox}
			}

		% callout idea
			\newcommand{\ideaCallout}[1]{\todo[color=Thistle, size=\small]{#1}}

	% guildline and direction
		\newcommand{\toWrite}[1]{\noindent
			\textcolor{Cyan}{\textbf{[[ #1 ]]}}}

	% call for help
		\newcommand{\callforhelp}[1]{\todo[color=SpringGreen]{#1}}
		\newcommand{\martin}[1]{\todo[color=SpringGreen]{@Martin:\\#1}}

@@

	\section{Non-trivial informational closure\martin{todo}}
		\ideaBox{I am still not sure we should go for NTIC without describe my intuition about consciousness and closure? Or we should start with my intuition. Or we should postpone to explain the intuition in Chapter 4?}

@@

		\subsection{\martin{todo}Neural coarse-graining}
			\begin{figure}
				\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
				\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
				\label{fig:NCG}				
			\end{figure}

@@

				@ Through two objectives during training, the model can achieve NTIC. \martin{todo}

@@

				@ \idea[red]{I need to somehow acknowledge \cite{pennartz2017consciousness}}
					@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}

@@

		\subsection{Sensory hierarchy and neural coarse-graining
			\todo[color=Red]{This is super important. I need to deal with this very carefully. Need to completely rewording}}\label{sec:SensoryHierarchy}

@@

				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \todo[color=red]{I NEED A EQUATION!}).

@@

					@@ \toWrite{Example from PID controller}

@@

					@ Because the forward model build on the informational closure representation can be seen as part of the closure. \todo[color=red]{IS THIS TRUE? NEED DISCUSSION}

@@

		\subsection{Finding coarse-grain function}
			\begin{ants}
				@ It's not clear what the coarse-graining function is.\todo[color=red]{this should be explained by environmental deterministic}

>>>>

% Meaning of colours --------------------------------------------------------- %
%	Red: Important and Critical
%	Orange: Todo
%	Blue: Topic and Guideline
%	Purple: Murmur
%	Green: Question, Call for help, Open for opinions and comments
%	Brown: Need Wording 
% ---------------------------------------------------------------------------- %

@@

% Funcitonal content
	% Quotes: green
		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}

	% todo: orange
		% text todo
		\newcommand{\toWrite}[1]{\noindent
			\textcolor{Orange}{\textbf{[[ #1 ]]}}}

		% figure todo
		\newcommand{\includegraphicsTodo}[2][]{%
			\tcbox[%
				adjusted title=\LARGE To Be Modified,
				halign title=right,
				colbacktitle=Orange!75!White,
				coltitle=Black,
				colframe=Red!60!White,
				boxrule=1mm,
				colback=white%
				]{\includegraphics[#1]{#2}}}

@@

		% Need reference 
		\newcommand{\needref}[1]{%
			\ifthenelse{\equal{#1}{}}{%
				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref}}}{%
				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref: #1}}%
			}%
		}

	% Highlight
		% Highlight only
		\newcommand{\highlight}[2][Thistle!50!white]{\colorbox{#1}{#2}}

		% Highlight and comment
		\newcommand{\highlightAndComment}[3][Thistle!50!white]{\todo[color=#1]{#3}\colorbox{#1}{#2}}

		% Critical point
		\newcommand{\critical}[1]{%
			\todo[color=OrangeRed!70!white]{#1}
		}

	% idea: Purple 
		% text idea
			\newcommand{\idea}[2][Plum]{\noindent
				\textcolor{#1}{[[ #2 ]]}}

		% box idea
			\newcommand{\ideaBox}[1]{
				\begin{tcolorbox}[%
					width=12cm,
					sharp corners=downhill, 
					hyphenationfix, 
					arc=8pt,
					colback=Thistle!50!white, 
					flush right,
					halign=flush right,
					]%
					#1
				\end{tcolorbox}
			}

		% callout idea
			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}

	% communication: green
		% call for help
			\newcommand{\callforhelp}[1]{\todo[color=SpringGreen]{[Call For Help]: #1}}

		% comment
			% comment by authers
			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}

			% usage: 
			% \addcomment{auther}{comment text} 
			% or
			% \addcomment[highlighted text]{auther}{comment text}
			%
			% e.g.
			% It's a \addcomment[beautiful]{Acer}{need a reference} day

@@

	\section{Non-trivial informational closure}
		\ideaBox{I am still not sure we should go for NTIC without describe my intuition about consciousness and closure? Or we should start with my intuition. Or we should postpone to explain the intuition in Chapter 4?}

@@

		\subsection{Neural coarse-graining}
			\begin{figure}
				\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
				\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
				\label{fig:NCG}				
			\end{figure}

@@

				@ Through two objectives during training, the model can achieve NTIC.

@@

				@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
					@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}

@@

		\subsection{Sensory hierarchy and neural coarse-graining
			\critical{This is super important. I need to deal with this very carefully. Need to completely rewording}}\label{sec:SensoryHierarchy}

@@

				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \critical{I NEED A EQUATION!}).

@@

					@@ \idea{Example from PID controller?}

@@

					@ Because the forward model build on the informational closure representation can be seen as part of the closure. \critical{IS THIS TRUE? NEED DISCUSSION}

@@

		\subsection{Finding coarse-grain function}
			\begin{ants}
				@ It's not clear what the coarse-graining function is.\critical{this should be explained by environmental deterministic}
